---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/c5sire/brapi?branch=master&svg=true)](https://ci.appveyor.com/project/c5sire/brapi)
[![Travis-CI Mac Build Status](https://travis-ci.org/c5sire/brapi.svg?branch=master&label=Mac%20OSX)](https://travis-ci.org/c5sire/brapi)

# README

An R package to use the [Breeding API (BrAPI)](http://docs.brapi.apiary.io) for accessing plant breeding data.

It can be installed using:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("c5sire/brapi")
```

The library implements currently mainly API calls to retrievie phenotypic field trial related data.

## Implementation status

API call | status
---------|-------
location |done
germplasm search | done
germplasm details|done
germplasm MCPD | in progress
germplasm pedigree |done
germplasm markerprofiles|done
program list |done
study list|done
study |done
study details|done
study layout|done
studies table|done

## How to use

See [tutorial](https://github.com/c5sire/brapi/blob/master/vignettes/tutorial.Rmd).







