---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# BrAPI R package 

## This version is still under development. The implementation sometimes changes minor details.

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# README

An R package to use the [Breeding API (BrAPI)](http://docs.brapi.apiary.io) for accessing plant breeding data.

It can be installed using:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("CIP-RIU/brapi")
```


## How to use the package

See [tutorial](https://github.com/c5sire/brapi/blob/master/inst/doc/tutorial.Rmd).

## Documentation of JSON response/requests


Follow the links in the table below or see the inst/apidocs directory for examples: [apidocs](https://github.com/c5sire/brapi/blob/master/inst/apidocs/README.md)

See the inst/apidocs directory for examples: [apidocs](https://github.com/c5sire/brapi/blob/master/inst/apidocs/README.md)


## Implementation status

See the inst/apidocs directory for examples: [apidocs](https://github.com/c5sire/brapi/blob/master/inst/apidocs/README.md)

