---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

--------------------------------------------------------------
This package is under development. It has not yet been exhaustively tested for all calls neither. Usage may also still change. If you have suggestions please use the issue tracker.
------------------------------------------------------------------------

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/c5sire/brapi?branch=master&svg=true)](https://ci.appveyor.com/project/c5sire/brapi)
[![Travis-CI Mac Build Status](https://travis-ci.org/c5sire/brapi.svg?branch=master&label=Mac%20OSX)](https://travis-ci.org/c5sire/brapi)
[![Coverage Status](https://img.shields.io/codecov/c/github/c5sire/brapi/master.svg)](https://codecov.io/github/c5sire/brapi?branch=master)

# README

An R package to use the [Breeding API (BrAPI)](http://docs.brapi.apiary.io) for accessing plant breeding data.

It can be installed using:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("c5sire/brapi")
```

The library implements currently mainly API calls to retrievie phenotypic field trial related data.

## Implementation status

```{r, echo=FALSE}
calls_data = tryCatch({
  read.csv(system.file("apps/brapi/data/calls.csv", package = "brapi"),
           stringsAsFactors = FALSE)
  
}, error = function(e) {
  NULL
}
)

res <- calls_data[stringr::str_detect(calls_data$clients, "brapi"), 1:4]

pct <- round(nrow(res) / nrow(calls_data) * 100, 1)
```

Out of `r nrow(calls_data)` BrAPI calls currently **`r nrow(res)` (`r pct`%)** are implemented in this package.

```{r, echo=FALSE}
knitr::kable(res, row.names = FALSE)

```



## How to use the package

See [tutorial](https://github.com/c5sire/brapi/blob/master/vignettes/tutorial.md).


```{r eval=FALSE, echo=FALSE}
rp =covr::package_coverage(function_exclusions =
    c("can_internet", "programs_list", "gp2tbl", "brapiConnectAddin", "mk2tbl",
      "loc2tbl", "brapi_con", "brapiConnectInput", "brapiPOST", "brapiConnect",
      "locations_list", "mock", "sgp2tbl", "sou2tbl", "lyt2tbl", "trl2tbl",
      "stdd2tbl", "ams2tbl", "sov2tbl",
      "germplasm_mcpd", "print.brapi", ".onLoad", "brapi_auth", "df2tibble"))

covr::report(rp)

```




