---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
# The official repository for the Breeding API (BraPi)implemenation in R 

## This version is still under development. The implementation sometimes changes minor details.

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# README

An R package to use the [Breeding API (BrAPI)](http://docs.brapi.apiary.io) for accessing plant breeding data.

It can be installed using:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("CIP-RIU/brapi")
```


## How to use the package

See [tutorial](https://github.com/c5sire/brapi/blob/master/inst/doc/tutorial.Rmd).

## Documentation of JSON response/requests

<<<<<<< HEAD
Follow the links in the table below or see the inst/apidocs directory for examples: [apidocs](https://github.com/CIP-RIU/brapi/blob/master/inst/apidocs/README.md)
=======
See the inst/apidocs directory for examples: [apidocs](https://github.com/CIP-RIU/brapi/blob/master/inst/apidocs/README.md)


## Implementation status
=======
See the inst/apidocs directory for examples: [apidocs](https://github.com/c5sire/brapi/blob/master/inst/apidocs/README.md)


>>>>>>> upstream/master

```{r, echo=FALSE}
# calls_data = tryCatch({
#   read.csv(system.file("apidocs/calls.csv", package = "brapi"),
#            stringsAsFactors = FALSE)
#   
# }, error = function(e) {
#   NULL
# }
# )
# 
# 
# 
# res <- calls_data[stringr::str_detect(calls_data$client.brapi, "x"), c(1, 7, 8)]
# 
# pct <- round(nrow(res) / nrow(calls_data) * 100, 1)
```

```{r, echo=FALSE}


#res[, 3] <- paste0("[", res[, 3], "](https://github.com/CIP-RIU/brapi/blob/master/inst/apidocs/", res[, 3], ".md)") 

#res[, 2] <- paste0("[", res[, 2], "](https://github.com/plantbreeding/API/blob/master/Specification/", res[, 1], "/", 
#                   res[, 2], ".md)") 
#res[, 1] <- paste0("[", res[, 1], "](https://github.com/plantbreeding/API/blob/master/Specification/", res[, 1], ")") 

#knitr::kable(res, row.names = FALSE)

```

```{r eval=FALSE, echo=FALSE}
#rp =covr::package_coverage()

#covr::report(rp)

###########################
owd <- getwd()
setwd("inst/apidocs")
mdfiles <- list.files(".", "*.Rmd")
sapply(mdfiles, knitr::knit)
setwd(owd)
```
